mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-08 EMSOFT2016/diff/0208_thesis.tex
update

The system model of mruby on TECS is shown in Figure \ref{fig:system_model}.
Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
    \caption{System Model}
    \label{fig:system_model}
\end{figure}

@@

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and MrubyBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:ht-tecs}.
The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.

@@

The size and transfer time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The bytecode of mruby application including library is larger and slower than that of only mruby application in terms of size and transfer time.
In the proposed framework, developers send only mruby application and prepare mruby library in advance.
Therefore, the design can send the bytecode faster.
In addition, the design can save the time to insert an SD card.
These advantages lead to improving the work efficiency.

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccc}
        & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
        Lua \cite{url:Lua}, \cite{par:Lua} &            & -          & \checkmark &            \\
        Owl system \cite{par:owl}                         &            & -          & -          & \checkmark \\
        mruby \cite{par:mruby}, \cite{url:mruby}                             &            &            & \checkmark &            \\
        mruby on TECS \cite{par:mrubyonTECS}                     &            & \checkmark & \checkmark &            \\
        Proposed framework& \checkmark & \checkmark & \checkmark &            \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
Lua \cite{url:Lua}, \cite{par:Lua}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

Lua is one of the most popular script languages for embedded systems.
Lua supports co-routine, referred to collaborative multitasking.
A co-routine in Lua is used as an independently executed thread.
A co-routine can just suspend and resume multiple routines.
Thus, a Lua co-routine is not like multitasks in multitask systems.

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip \cite{url:python-on-a-chip}.
python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
GIL locks a CPU in order to prevent the non-thread-safe code from sharing the other threads.
GIL leads the limitation of the concurrency on multitasking.

>>>>

The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyontecs.pdf}
    \caption{System Model of existing mruby on TECS}
    \label{fig:mrubyontecs}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
    \caption{Specific System Model of the proposed framework}
    \label{fig:system_model}
\end{figure}

@@

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and MrubyBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.

@@

The size and transfer time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The bytecode of mruby application including library is larger and slower than that of only mruby application in terms of size and transfer time.
In the proposed framework, developers send only mruby application and prepare mruby library in advance.
Therefore, the design can send the bytecode faster.
In addition, the design can save the time to insert an SD card to restart an OS.
These advantages lead to improving the work efficiency.

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|cccccc}
        & Bluetooth Loader & \shortstack{Call\\C function} & \shortstack{Legacy code of\\embedded system} & VM managenment & \shortstack{Synchronization of\\application} & Co-routine \\ \hline
        Lua \cite{url:Lua}, \cite{par:Lua}           &            & \checkmark & Partially  &            &            & \checkmark \\
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &            & \checkmark \\
        mruby \cite{par:mruby}, \cite{url:mruby}     &            & \checkmark &            &            &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
eLua \cite{url:eLua},  python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

eLua offers the full implementation of Lua programming language to the embedded systems.
Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
Lua supports co-routine, referred to collaborative multitasking.
A co-routine in Lua is used as an independently executed thread.
A co-routine can just suspend and resume multiple routines.
Thus, a Lua co-routine is not like multitasks in multitask systems.

python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
The VM runs a significant subset of Python language with few resources on a microcontroller.
p14p can run multiple stackless green threads.

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip.
